%!TEX root=../thesis.tex
\pagebreak
\section{Security}
The following sections introduce the computer security terms, which are needed for this thesis.

\paragraph{Security Goals}
There are three main security goals: confidentiality, integrity and availability~\cite{pfleeger2015security}.
Confidentiality means that information is kept private and just accessable by authorized entities.
Integrity means that unauthorized modification of information is detectable and availability means that a service or data is available and usable~\cite{pfitzmann2012security}.
These goals can be achieved through different techniques, confidentiality for example can be achieved by using encryption.

\paragraph{Symmetric Encryption}
Symmetric encryption describes the class of encryption algorithms, where the same secret is used for encryption and decryption.
The communication partners that want to achieve confidentiality, therefore, they need a shared secret~\cite{pfitzmann2012security}.

\paragraph{Message Authentication Code}
A message authentication code is a symmetric system to check if a message has been manipulated by an unauthorized entity.
Message authentication codes help to achieve integrity.
Authorized entities need a shared secret to create and verify a message authentication code~\cite{pfitzmann2012security}.

\paragraph{Denial-of-Service}
A denial of service attack is an attack targeting the availability of data or a service.
One example for a Denial-of-Service attack is the flooding of a network with unneccessary information to overload it~\cite{pfleeger2015security}.

\paragraph{Replay attack}
Another attack is the replay attack.
Here the attacker delays or repeats valid messages between two parties to gain information~\cite{pfleeger2015security}.
